---
title: "Speed of light app"
author: "Jhonatan Zambrano"
date: "3/12/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Dataset

The dataset used for develop the app contains 100 measurements of the speed of 
light from five experiments, each of this consisting of 20 consecutive "runs".

The speed of light is coded in km/sec with 299000 subtracted.

```{r data, message=F, comment=""}
library(datasets)
df<-morley
df$Expt<-as.factor(df$Expt)
head(df, 5)
summary(df)
```



## The data selection

The user is able to exclude the more extreme values using two limits values: 
the inferior quantile and the superior quantile, this is achieved obtaining from 
the user the desired quantile and calculating the corresponding speed value. 
It's shown in the graph as blue lines:

```{r graph1, fig.align='center'}
library(ggplot2)
ggplot(data = df, aes(x=as.numeric(rownames(df)), y=Speed))+
  geom_point(aes(color=Expt))+
  geom_abline(slope=0, intercept = mean(df$Speed), color ="red")+
  geom_abline(slope=0, intercept = quantile(df$Speed, 0.05), color ="blue")+
  geom_abline(slope=0, intercept = quantile(df$Speed, 0.95), color ="blue")+
  ggtitle("Plot of all data")+
  xlab("overall sample number")+
  labs(caption = "here we use 0.05 and 0.95 quantiles")
```

## Plots

After selecting the data, the user can generate the following additional plots:

- Boxplot: a boxplot segregated by experiments
- Histogram: a histogram which can be modified by changing their bins
- Density: a probability density plot using a gaussian kernel, the user can select to see the overall behavior or by experiment.

## Boxplot

```{r graph2, fig.align='center'}
ggplot(data = df, aes(y=Speed))+
  geom_boxplot(aes(color = Expt))+
  ggtitle("Speed of Light, by experiments")
```

## Histogram

```{r graph3, fig.align='center'}
ggplot(data = df, aes(x=Speed))+
  geom_histogram(bins=6)
```

## Density

```{r graph4, fig.align='center'}
ggplot(data = df, aes(x=Speed))+
  geom_density(aes(color = Expt))
```